Is Archaeology a science? Insights and imperatives from 10,000 articles and a year of reproducibility reviews

### 2025-06-05 analysis/paper/paper.qmd
remove mention of supplementary materials

The entire R code [@rcoreteamLanguageEnvironmentStatistical2024] used for all the analysis and visualizations contained in this paper is at https://doi.org/10.5281/zenodo.14897253 to enable re-use of materials and improve reproducibility and transparency [@marwickComputationalReproducibilityArchaeological2017]. All the figures, tables, and statistical test results presented here can be independently reproduced with the code and data in this compendium [@doi:10.1080/00031305.2017.1375986]. The R code is released under the MIT license, the data as CC-0, and figures as CC-BY, to enable maximum re-use.

@@

```{r}
#| label: fig-change-over-time
#| fig-cap: Distribution of article characteristics for archaeology articles over time. Data points represent individual articles. The colour of the points indicates if the overall trend is toward softer (orange) or harder (green). Bayesian Generalized Additive Models were computed to fit the lines summarising the relationships between the variables and the time series. For recency of references a Zero-One Inflated Beta distribution family was used with a logit link function. For diversity of references and relative title length (ln) the Gaussian family was used with the canonical identity link function. For the number of authors pages the Negative Binomial family was used with a standard log link function. Further details about the model specifications and diagnostics are presented in the supplementary materials. 
#| fig-height: 6

@@

The data that support the findings of this study are openly available in Zenodo at http://doi.org/10.5281/zenodo.14897253

>>>>

The entire R code [@rcoreteamLanguageEnvironmentStatistical2024] used for all the analysis and visualizations contained in this paper is at https://doi.org/10.5281/zenodo.14897252 to enable re-use of materials and improve reproducibility and transparency [@marwickComputationalReproducibilityArchaeological2017]. All the figures, tables, and statistical test results presented here can be independently reproduced with the code and data in this compendium [@doi:10.1080/00031305.2017.1375986]. The R code is released under the MIT license, the data as CC-0, and figures as CC-BY, to enable maximum re-use.

@@

```{r}
#| label: fig-change-over-time
#| fig-cap: Distribution of article characteristics for archaeology articles over time. Data points represent individual articles. The colour of the points indicates if the overall trend is toward softer (orange) or harder (green). Bayesian Generalized Additive Models were computed to fit the lines summarising the relationships between the variables and the time series. For recency of references a Zero-One Inflated Beta distribution family was used with a logit link function. For diversity of references and relative title length (ln) the Gaussian family was used with the canonical identity link function. For the number of authors pages the Negative Binomial family was used with a standard log link function. Further details about the model specifications and diagnostics are available at https://doi.org/10.5281/zenodo.14897252  
#| fig-height: 6

@@

The data that support the findings of this study are openly available in Zenodo at https://doi.org/10.5281/zenodo.14897252
